Fail Faster

### 2025-03-22 paper/paper.tex
update figs
change colors
new graph

\begin{figure}[h]
  % \includegraphics[scale=0.33]{allocs.png}
  \includegraphics[scale=0.32]{time.png}
  \caption{Time to generate using each strategy. Performance benefits scale with generation size (lower lines translate to greater performance benefit). BQ is \bq; Staged SR is \camlname using \bq's \texttt{splittable\_random} RNG; Staged CSR is \camlname using \secref{subsection:faster-rng}'s \csplitmix.}
  \label{fig:time}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.46]{scala.png}
 \caption{
  \jwc{Don't explain the chart in the caption, split this into two different charts --- purple on one, green on the other.}
  \jwc{Also can we use the language's colors for this?}
  \scalaname has better performance relative to ScalaCheck than \camlname relative to \bq. SC is ScalaCheck; BQ is \bq. Comparison is for a fixed size of 100.}
 \label{fig:scala}
 \end{figure}

@@

The average individual-task speedups for each strategy and benchmark are shown in
\figref{fig:etna}, with trends in bug-finding speed closely mirroring those in performance
from \secref{subsection:benchmarking}. The distribution of speedups in \figref{fig:swarm} reveals
substantial variability, with most tasks clustering near the median and a long tail of outliers
achieving much larger gains. STLC shows a more bimodal distribution of speedups
than the other benchmarks, which we attribute to the heterogenous difficulty of its tasks:
some tasks regularly hit the 60-second timeout, while others finish in a fraction of a second. We
find that ``easier'' tasks---those that run on the order of milliseconds---regularly achieve speedups in the
range of 4--9x, whereas tasks that run on the order of seconds achieve more moderate speedups of up to 3.5x.
Overall,
these results give strong evidence that \camlname consistently benefits bug-finding speed, sometimes drastically.
\begin{figure}[h]
  \includegraphics[scale=0.3]{speedup.png}
  \caption{Geometric average of all speedups---relative to BQ---for each strategy and benchmark, showing that staging leads to better bug-finding speed across the board.
  \jwc{Charts start at one? Can eliminate the BQ bar}
  }
  \label{fig:etna}
\end{figure}
\begin{figure}[h]
  \includegraphics[scale=0.31]{swarm.png}
  \caption{Swarm distribution of individual-task speedups across strategies and benchmarks---gray dots represent tasks. Plots with extremely low variance have no swarm overlay; in plots with high variance, outliers correspond to large speedups. \tr{Make mean higher-contrast.}}
  \label{fig:swarm}
\end{figure}

@@

  \item \textbf{F#} 
  % https://learn.microsoft.com/en-us/dotnet/fsharp/language-reference/code-quotations

>>>>

\begin{figure}[h]
  % \includegraphics[scale=0.33]{allocs.png}
  \includegraphics[scale=0.43]{time.png}
  \caption{Time to generate values of varying sizes using each \camlname strategy. Lower lines translate to greater performance benefit. BQ is \bq; Staged SR is \camlname using \bq's \texttt{splittable\_random} RNG; Staged CSR is \camlname using \csplitmix.}
  \label{fig:time}
\end{figure}

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.49]{scala.png}
 \caption{Time to generate values of varying sizes using each \scalaname strategy. SC is ScalaCheck; Staged is \scalaname.}
 \label{fig:scala}
 \end{figure}

@@

The average individual-task speedups for each strategy and benchmark are shown in
\figref{fig:etna}, with trends in bug-finding speed closely mirroring those in performance
from \secref{subsection:benchmarking}. The distribution of speedups in \figref{fig:swarm} reveals
substantial variability, with most tasks clustering near the median and a long tail of outliers
achieving much larger gains. STLC shows a more bimodal distribution of speedups
than the other benchmarks, which we attribute to the heterogenous difficulty of its tasks:
some tasks regularly hit the 60-second timeout, while others finish in a fraction of a second. We
find that ``easier'' tasks---those that run on the order of milliseconds---regularly achieve speedups in the
range of 4--9x, whereas tasks that run on the order of seconds achieve more moderate speedups of up to 3.5x.
Overall,
these results give strong evidence that \camlname consistently benefits bug-finding speed, sometimes drastically.
\begin{figure}[h]
  \includegraphics[scale=0.3]{speedup.png}
  \caption{Geometric average of all speedups---relative to BQ---for each strategy and benchmark, showing that staging leads to better bug-finding speed across the board.
  }
  \label{fig:etna}
\end{figure}
\begin{figure}[h]
  \includegraphics[scale=0.31]{swarm.png}
  \caption{Distribution of individual-task speedups across strategies and benchmarks. Gray dots represent tasks. Plots with extremely low variance have no swarm overlay; in plots with high variance, outliers correspond to large speedups.}
  \label{fig:swarm}
\end{figure}

@@

  \item \textbf{F\#} 
  % https://learn.microsoft.com/en-us/dotnet/fsharp/language-reference/code-quotations
